Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-21 manuscript/manuscript.tex
Add first approach to results and discussion

>>>>

\section{Results and Discussion}

The $D$ and $\delta$ ratios determinations proved that for a linear density case only
the two dimensional adaptive discretization algorithm and a second-order GLQ
approximation is needed to achieve a 0.1\% accuracy of the gravitational potential and
the vertical component of the gradient ($g_z$) by using a $D=$ 1 and 2.5 for each field,
respectively.
Although for non-linear functions the adaptive discretization is not sufficient and the
density-based discretization algorithm must be applied.
The $D$-$\delta$ space exploration showed that the more efficient computation takes
place when the value of $D$ equals to the ones determined in the linear density
scenario, while the value of $\delta$ must be determined for each specific density
variation.
In case of an exponential density, a $\delta$ equal to 0.1 is sufficient to achieve the
0.1\% accuracy threshold, while a $\delta = 0.01$ is needed for a sinusoidal density
function.

This result could be extrapolated: a default value of $\delta = 0.01$ would guarantee an
accuracy of 0.1\% in case of an arbitrary continuous density function.
Nevertheless, we encourage to perform similar accuracy tests in order to proof that this
extrapolation works for the desired density function, specially for more complex
variations than a polynomial or exponential one.

\citet{Lin2018} proposed a combined method to efficiently compute gravitational fields
generated by tesseroids: it uses a GLQ with a two dimensional adaptive discretization
algorithm for near computation points and a Taylor series expansion method for far
computation points.
Because our goal is to build a method that could be applied to any continuous density
function, the Taylor series wouldn't be well suited for this task and therefore we
focused only on a pure GLQ approximation method.
Nevertheless, our method could be easily combined with a Taylor series expansion for
specific density function, i.e.~a linear variation.

Moreover, \citet{Lin2018} show that the combined method can be applied to a linear
density variation by splitting the gravitational field integral in two: one for each
term of the linear function.
Our results show that in case of a linear density variation a single GLQ computation is
sufficient to accurately compute the fields, thus reducing the computation time by half.

\citet{Fukushima2018} propose a generalization of his method to polynomial density
functions.
On the other hand, our method is not bounded to a specific density function.
Nevertheless, the density-based discretization algorithm could be used before applying
the numerical integration developed by \citet{Fukushima2018} assigning a low polynomial
order density to each discretizing tesseroid.
Although this method would involve a computational error due to the approximation of the
density function as a polynomial one, it's feasibly if we account for this error and
a method to limit it.

We have also carried out $D$ and $\delta$ determinations for the vertical component of
the Marussi tensor ($g_{zz}$) for linear and exponential densities.
We didn't include these results because our methodology wouldn't achieve the 0.1\%
accuracy threshold for the general case of such density functions.
Moreover, the values of $D$ and $\delta$ needed for the cases at which the accuracy was
below 0.1\% implied a high number of discretizations, thus greatly increasing the
computation time.
In summary, we found the computation of the Marussi tensor components in case of
variable density tesseroids a subject for future research.
